gij bent 2

### 2024-12-11 paper/paper.qmd
Add a suggestion for a conclusion

>>>>

This article aimed to investigate whether and how speakers deviate from general expectations. We focussed on the affordances these deviations, defined as individual variation, can bring for alternation research, as well as what implicit network structures can teach us about the spread of linguistic innovations. We looked into the choice between the conservative *gij zijt* and the innovative *gij bent* in Colloquial Belgian Dutch with a dataset based on `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` authors. By having several attestations from the same authors, we were able to devise a "linguistic profile" for each author, quantifying their behaviour with regards to expectations based on more general factors like gender and dialect region. Through elastic net regression, a modern regression technique, deviations were found for TODO users in the dataset (TODO percent). TODO more conservative, TODO more innovative We also found a regional pattern in the deviations, with the central Brabant region differing from the other Flemish dialects. The Brabant region deviates towards the innovative form, the other regions deviate towards the conservative form. We also found a geospatial pattern, spanning horizontally, which shows a potential future path for the diffusion of the innovative form.

The consequences of our findings are twofold. In a broad sense, our results show that individual variation exists, and in fact is abundant in our case. This illustrates that an important dimension of variation is likely lost in traditional regression models. The regional and geospatial patterns in our data show that if people deviate from the general patterns we expect, this deviation is not random. In a sense, it means that there is "second order variation", variation *within* the variation, so to say. The geospatial distribution also provides an opportunity to anticipate upcoming diffusion patterns. Of course, we should not treat these patterns as oracles, but they can be useful nonetheless.

The predictive nature of the geospatial distributions bring us to the network analysis of our study. Our results show that the socially influential users in our dataset are generally more innovative. This might indicate that the diffusion of the innovative *bent* variant is in the TODO phase.
